Exploring mathematical objects from custom-tailored mathematical universes

### 2020-12-27 paper-herrsching2019/generalized-spaces.tex
typo
Absolute final version

\documentclass{ws-rv9x6}
\usepackage[onethmnum]{ws-rv-thm}
\usepackage{ws-rv-van}

@@

@@

Section~\ref{sect:locales} explores the basics of the theory of locales, with a
focus on examples and issues for constructive mathematics. Accessible
introductions to the theory include
Refs.~\refcite{johnstone:art,johnstone:point}. The interplay between logic and
geometry is particularly stressed in
Refs.~\refcite{vickers:continuity,vickers:locales-toposes}. We recommend
Ref.~\refcite{belanger-marquis:pointless} for a historical guide and
Ref.~\refcite{picado-pultr:frames-and-locales} for a comprehensive modern
textbook on the subject.

@@

Regarding constructive algebra, there are by now several
textbooks~\cite{mines-richman-ruitenburg:constructive-algebra,lombardi-quitte:constructive-algebra,yengui:constructive-commutative-algebra}
on constructive algebra available and there is a vast literature on
the intriguing subject of constructivizing classical commutative algebra.
Starting points include
Refs.~\refcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,rinaldi-schuster-wessel:edde,cederquist-coquand:entrel}.

\paragraph{Notes for readers familiar with the themes of this contribution.}
We present a self-contained proof of the simple
version of Barr's theorem as Theorem~\ref{thm:baby-barr}. For reducing
intuitionistic provability to geometric provability, we employ (what amounts
to) the syntactic site, similar to the refined completeness result
by Thierry Coquand~\cite{coquand:site} but closer to the standard description
of the syntactic site. For reducing classical provability to intuitionistic
provability, we employ a variant of the double negation translation. We were
not able to track down a reference to this approach in the context of
infinitary logic, but the basic idea has long been known and is summarized, for
instance, in Ref.~\refcite{aczel:russell-prawitz}.

@@

\paragraph{Compactness of the unit interval.} The unit interval, when realized
as a topological space, can fail to be compact in constructive
mathematics. For instance, it fails in the Russian school because the Kleene
tree provides a computable open covering of~$[0,1]$ with no computable finite
subcovering (a self-contained exposition of this phenomenon is contained in
Ref.~\refcite{bauer:kleene-tree}).

@@

To verify that~(2) implies~(1), we define a semantics~``$\alpha \models
\varphi$'' for geometric formulas~$\alpha$ and infinitary first-order
formulas~$\varphi$ by the clauses in Table~\ref{table:classifying-topos}. For
notational simplicity, we restrict to the propositional case, that is assume that the set of
sorts of~$\TT$ is empty.
The following properties of the semantics can then be established by induction:
\begin{alphlist}[(d)]
\item If~$\TT$ proves~$\beta \vdash \alpha$ (in geometric logic), then~$\alpha \models \varphi$ implies~$\beta
\models \varphi$.
\item If~$\TT$ proves~$\alpha \dashv\vdash \bigvee_i \beta_i$ (geometrically) and if~$\beta_i \models \varphi$ for
all indices~$i$, then~$\alpha \models \varphi$.
\item\label{item:baby-geom} If~$\varphi$ is a geometric formula, then~$\alpha
\models \varphi$ iff~$\TT$ proves~$\alpha \vdash \varphi$ (geometrically).
\item\label{item:baby-sound} If a first-order sequent~$(\varphi \vdash \psi)$
is derivable from the axioms of~$\TT$ in infinitary intuitionistic logic,
then~$\top \models (\varphi \Rightarrow \psi)$.
\end{alphlist}
We can then conclude as follows. Assume that~$(\varphi \vdash \psi)$
is derivable in infinitary intuitionistic logic. By~(\ref{item:baby-sound}), we
have~$\top \models (\varphi \Rightarrow \psi)$. By the clause for implication
in Table~\ref{table:classifying-topos}, we have~$\varphi \models \psi$.
By~(\ref{item:baby-geom}), there is a~$\TT$-derivation of~$\varphi \models
\psi$ in geometric logic.
\end{proof}

\begin{remark}The semantics set up in the proof of Theorem~\ref{thm:baby-barr}
coincides with the sheaf semantics of the \emph{classifying locale} of~$\TT$
reviewed in Section~\ref{sect:presenting-frames} and
Section~\ref{sect:sheaf-semantics}. In the nonpropositional case, the semantics
coincides with the slightly more general topos semantics of the
\emph{classifying topos} of~$\TT$~\cite[Section~2]{caramello:tst}. The local
operator defined in the proof cuts out a certain Boolean subtopos of the
classifying topos. An alternative proof proceeds by cut
elimination~\cite[Section~6]{rathjen:barr}; see also
Ref.~\refcite{dyckhoff-negri:geometrisation}, and
Ref.~\refcite{rathjen-toppel:reduction} for background on proof-theoretical
reduction, of which Barr's theorem is an example.
\end{remark}

@@

When first learning about presheaves, one may feel intimidated by the vast
amount of data encoded in a single presheaf (one set for each open, of which there are often uncountably many). The
situation should be compared to the perhaps more familiar Kripke models for a first-order language~$L$. The
preorder~$W$ of nodes of such a model is like the frame of opens of a locale, and the
family~$(M_w)_{w \in W}$ of~$L$-structures, one for each node, is like a
presheaf. In fact, the notion of a locale can be generalized to that of a
\emph{site} so that both locales and Kripke frames induce sites and that
presheaves on sites can be defined; however, this shall not be pursued here,
a textbook reference is Ref.~\refcite{moerdijk-maclane:sheaves-logic}.

@@

We now begin the formal development of the sheaf semantics. More background and
examples from theoretical computer science, analysis and differential geometry
are contained in Ref.~\refcite{blechschmidt:custom-tailored}, which should be
regarded as a companion paper to this contribution. We also recommend
Christopher Mulvey's tutorial~\cite{mulvey:repr}, which culminates in a proof
of the Serre--Swan theorem using the sheaf semantics. Standard references for
the sheaf semantics include Refs.
\cite[Chapter~VI]{moerdijk-maclane:sheaves-logic},
\cite[Chapter~14]{goldblatt:topoi},
\cite[Section~5]{caramello:preliminaries},
\cite[Sections~12--15]{streicher:ctcl},
\cite[Chapter~6]{borceux:handbook3},
\cite[Part~D]{johnstone:elephant} and~[\refcite{shulman:categorical-logic}],
which also gives a detailed account of useful type theory.

@@

Definition~\ref{defn:anonymously-noetherian} is at odds with the idea that constructive mathematics should
be informative: It only expresses that it is impossible for no finite
generating family to exist without requiring that such a family should be given
-- it may remain \emph{anonymous}.\footnote{We borrowed the term ``anonymous''
from type theory, where it is used with a similar meaning (see for instance
Ref.~\refcite{kraus-escardo-coquand-altenkirch:anonymous}). However, there is a
subtle difference: The conjunction of ``there is at most one element~$x$'' and
``there is anonymously an element~$x$ in the sense of type theory'' implies
that there actually exists an element~$x$. In contrast, \notnot existence does
not.} And while Hilbert's basis theorem, stating that if a ring~$B$ is
Noetherian then so is the polynomial ring~$B[X]$, does have a constructive
proof for the anonymous version of the Noetherian condition,\footnote{For
instance, a careful reading of the textbook proof given
in~\cite[Theorem~7.5]{atiyah-macdonald:commutative-algebra} shows that the
basis theorem holds intuitionistically as stated.} this result seems empty: For
it just transforms one unconcrete promise (generators of each ideal of~$B$
exist somewhere, platonically) into another (generators for ideals of~$B[X]$
exist somewhere, platonically).

@@

\begin{remark}Given the importance of Theorem~\ref{thm:workhorse}, it is
natural to wonder where the proof stems from. Our proof proceeded in an ad hoc
fashion, verifying that the frame of radical ideals has the required properties
-- but where does the idea to use radical ideals come from? In general, determining the set
of provable sequents of a geometric theory is a challenging problem. Our most
efficient tool is probably the theory of \emph{entailment relations}. We refer
to Refs.~\refcite{rinaldi-schuster-wessel:edde,cederquist-coquand:entrel} and
the references therein and also strongly recommend the literature on dynamical
methods in commutative
algebra~\refcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,coquand:site}.
\end{remark}

@@

\paragraph{Grothendieck's generic freeness lemma.} This theorem is a basic
theorem in algebraic geometry, used for instance for developing the theory of
moduli spaces. When phrased for the affine situation in a constructively
sensible way, a simple version of this theorem reads as follows. We recall
from Section~\ref{sect:algebraic-preliminaries} that
the notation~$M[f^{-1}]$ makes sense for any element~$f \in A$; in case~$f$ is
zero or nilpotent, the localized module~$M[f^{-1}]$ will be the trivial module.\par
\begin{quote}
\textbf{Theorem.}
Let~$A$ be a reduced ring. Let~$M$ be a finitely generated~$A$-module.
If~$f = 0$ is the only element of~$A$ such that~$M[f^{-1}]$ is a
free~$A[f^{-1}]$-module, then~$1 = 0$ in~$A$.
\end{quote}
This theorem is particularly interesting for the program of constructivizing
classical commutative algebra, as it is an example where the constructive proof
is much shorter and arguably more perspiciuous than classical proofs (for which
see for instance Refs.~\cite[Lemme~6.9.2]{ega-4-2},
\cite[Thm.~24.1]{matsumura:commutative-ring-theory} or
\cite[Thm.~14.4]{eisenbud:commutative-algebra}, which only cover the case of
Noetherian integral domains, or Refs.~[\refcite{staats:generic-freeness}],
\cite[Tag~051Q]{stacks-project}
which proceed in a series of intermediate steps, reducing to that case).\par
\begin{quote}
\textbf{Proof.} By Example~\ref{ex:negneg-interpretation} and
Exercise~\ref{ex:bridging-modules}(\ref{item:free}), the claim amounts to the statement that~$M^\sim$ is \notnot
free. Since~$A^\sim$ is a field, this statement follows from
basic (intuitionistic) linear algebra.\footnote{A standard result of linear
algebra is: ``Any finitely generated vector space over a field is finite free
(that is, has a finite basis).'' The proof proceeds by considering a given
generating family and using the law of excluded middle to determine whether one
of the generators can be expressed using the others or not. In the latter case,
the family is linearly independent and hence a basis; in the former case, the
proof removes the redundant generator and continues by induction.

@@

Item~(1) is by basic linear algebra as in the proof of
simple version of Grothendieck's generic freeness lemma, but a bit more involved as we now need to
deal with countable generating
families~\cite[Theorem~11.16]{blechschmidt:phd}. Item~(2) is because finitely
generated algebras over anonymously Noetherian rings are \notnot finitely
presented (in a description of the form~$R[X_1,\ldots,X_n]/\aaa$, the
ideal~$\aaa$ is \notnot finitely generated).
Item~(3) is because finitely generated modules over anonymously Noetherian are
\notnot finitely presented.\qed
\end{quote}
A variant of this proof where the reference to the Noetherian condition has
been replaced by an explicit computation has been unwound in
Ref.~\refcite{blechschmidt:generic-freeness}.

@@

Other short and explicit proofs of McCoy's theorem are given in
Refs.~\refcite{blocki:mccoy},
\cite[Theorem~5.22]{lombardi-quitte:constructive-algebra} and
\cite[Exercise~5.23A(3)]{lam:exercises}. The proof in
Ref.~\cite[Proposition~III.8.2.3]{bourbaki:alg} employs the law of excluded
middle. We were not able to discern that these proofs are just different
presentations of the same idea that ours is based on; these proofs all employ
computations with Cramer-like formulas, while our proof stresses the similarity
to the field case.

@@

The for these purposes correct constructive notion of Krull dimension can be
found in Refs.~\refcite{coquand-ducos-lombardi-quitte:krull-integral,coquand-lombardi-roy:char-krull}.
It has been used to give a short and constructive proof that~$\dim
k[X_1,\ldots,X_n] = n$, where~$k$ is a geometric
field~\cite{coquand-lombardi:krull-dim-polynomial-ring}. Proofs of the stated
relation between the dimension of~$A$ and the dimension of~$A^\sim$ are recorded in
Ref.~\cite[Section~3.4]{blechschmidt:phd}.\par}
\end{exercise}

@@

{\scriptsize\emph{Note.} A self-contained solution is given in
Ref.~\refcite{blechschmidt:kaplansky}.\par}
\end{alphlist}
\end{exercise}

>>>>

\documentclass{ws-rv9x6}
\usepackage[onethmnum]{ws-rv-thm}
\usepackage[square]{ws-rv-van}

@@

\newcommand{\bracketedrefcite}[1]{\citep{#1}}

@@

Section~\ref{sect:locales} explores the basics of the theory of locales, with a
focus on examples and issues for constructive mathematics. Accessible
introductions to the theory include
Refs.~\bracketedrefcite{johnstone:art,johnstone:point}. The interplay between logic and
geometry is particularly stressed in
Refs.~\bracketedrefcite{vickers:continuity,vickers:locales-toposes}. We recommend
Ref.~\bracketedrefcite{belanger-marquis:pointless} for a historical guide and
Ref.~\bracketedrefcite{picado-pultr:frames-and-locales} for a comprehensive modern
textbook on the subject.

@@

Regarding constructive algebra, there are by now several
textbooks~\cite{mines-richman-ruitenburg:constructive-algebra,lombardi-quitte:constructive-algebra,yengui:constructive-commutative-algebra}
on constructive algebra available and there is a vast literature on
the intriguing subject of constructivizing classical commutative algebra.
Starting points include
Refs.~\bracketedrefcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,rinaldi-schuster-wessel:edde,cederquist-coquand:entrel}.

\paragraph{Notes for readers familiar with the themes of this contribution.}
We present a self-contained proof of the simple
version of Barr's theorem as Theorem~\ref{thm:baby-barr}. For reducing
intuitionistic provability to geometric provability, we employ (what amounts
to) the syntactic site, similar to the refined completeness result
by Thierry Coquand~\cite{coquand:site} but closer to the standard description
of the syntactic site. For reducing classical provability to intuitionistic
provability, we employ a variant of the double negation translation. We were
not able to track down a reference to this approach in the context of
infinitary logic, but the basic idea has long been known and is summarized, for
instance, in Ref.~\bracketedrefcite{aczel:russell-prawitz}.

@@

\paragraph{Compactness of the unit interval.} The unit interval, when realized
as a topological space, can fail to be compact in constructive
mathematics. For instance, it fails in the Russian school because the Kleene
tree provides a computable open covering of~$[0,1]$ with no computable finite
subcovering (a self-contained exposition of this phenomenon is contained in
Ref.~\bracketedrefcite{bauer:kleene-tree}).

@@

To verify that~(2) implies~(1), we define a semantics~``$\alpha \models
\varphi$'' for geometric formulas~$\alpha$ and infinitary first-order
formulas~$\varphi$ by the clauses in Table~\ref{table:classifying-topos}. For
notational simplicity, we restrict to the propositional case, that is assume that the set of
sorts of~$\TT$ is empty.
The following properties of the semantics can then be established by induction:
\begin{alphlist}[(d)]
\item If~$\TT$ proves~$\beta \vdash \alpha$ (in geometric logic), then~$\alpha \models \varphi$ implies~$\beta
\models \varphi$.
\item If~$\TT$ proves~$\alpha \dashv\vdash \bigvee_i \beta_i$ (geometrically) and if~$\beta_i \models \varphi$ for
all indices~$i$, then~$\alpha \models \varphi$.
\item\label{item:baby-geom} If~$\varphi$ is a geometric formula, then~$\alpha
\models \varphi$ iff~$\TT$ proves~$\alpha \vdash \varphi$ (geometrically).
\item\label{item:baby-sound} If a first-order sequent~$(\varphi \vdash \psi)$
is derivable from the axioms of~$\TT$ in infinitary intuitionistic logic,
then~$\top \models (\varphi \Rightarrow \psi)$.
\end{alphlist}
We can then conclude as follows. Assume that~$(\varphi \vdash \psi)$
is derivable in infinitary intuitionistic logic. By~(\ref{item:baby-sound}), we
have~$\top \models (\varphi \Rightarrow \psi)$. By the clause for implication
in Table~\ref{table:classifying-topos}, we have~$\varphi \models \psi$.
By~(\ref{item:baby-geom}), there is a~$\TT$-derivation of~$\varphi \vdash
\psi$ in geometric logic.
\end{proof}

\begin{remark}The semantics set up in the proof of Theorem~\ref{thm:baby-barr}
coincides with the sheaf semantics of the \emph{classifying locale} of~$\TT$
reviewed in Section~\ref{sect:presenting-frames} and
Section~\ref{sect:sheaf-semantics}. In the nonpropositional case, the semantics
coincides with the slightly more general topos semantics of the
\emph{classifying topos} of~$\TT$~\cite[Section~2]{caramello:tst}. The local
operator defined in the proof cuts out a certain Boolean subtopos of the
classifying topos. An alternative proof proceeds by cut
elimination~\cite[Section~6]{rathjen:barr}; see also
Ref.~\bracketedrefcite{dyckhoff-negri:geometrisation}, and
Ref.~\bracketedrefcite{rathjen-toppel:reduction} for background on proof-theoretical
reduction, of which Barr's theorem is an example.
\end{remark}

@@

When first learning about presheaves, one may feel intimidated by the vast
amount of data encoded in a single presheaf (one set for each open, of which there are often uncountably many). The
situation should be compared to the perhaps more familiar Kripke models for a first-order language~$L$. The
preorder~$W$ of nodes of such a model is like the frame of opens of a locale, and the
family~$(M_w)_{w \in W}$ of~$L$-structures, one for each node, is like a
presheaf. In fact, the notion of a locale can be generalized to that of a
\emph{site} so that both locales and Kripke frames induce sites and that
presheaves on sites can be defined; however, this shall not be pursued here,
a textbook reference is Ref.~\bracketedrefcite{moerdijk-maclane:sheaves-logic}.

@@

We now begin the formal development of the sheaf semantics. More background and
examples from theoretical computer science, analysis and differential geometry
are contained in Ref.~\bracketedrefcite{blechschmidt:custom-tailored}, which should be
regarded as a companion paper to this contribution. We also recommend
Christopher Mulvey's tutorial~\cite{mulvey:repr}, which culminates in a proof
of the Serre--Swan theorem using the sheaf semantics. Standard references for
the sheaf semantics include Refs.
\cite[Chapter~VI]{moerdijk-maclane:sheaves-logic},
\cite[Chapter~14]{goldblatt:topoi},
\cite[Section~5]{caramello:preliminaries},
\cite[Sections~12--15]{streicher:ctcl},
\cite[Chapter~6]{borceux:handbook3},
\cite[Part~D]{johnstone:elephant} and~\bracketedrefcite{shulman:categorical-logic},
which also gives a detailed account of useful type theory.

@@

Definition~\ref{defn:anonymously-noetherian} is at odds with the idea that constructive mathematics should
be informative: It only expresses that it is impossible for no finite
generating family to exist without requiring that such a family should be given
-- it may remain \emph{anonymous}.\footnote{We borrowed the term ``anonymous''
from type theory, where it is used with a similar meaning (see for instance
Ref.~\bracketedrefcite{kraus-escardo-coquand-altenkirch:anonymous}). However, there is a
subtle difference: The conjunction of ``there is at most one element~$x$'' and
``there is anonymously an element~$x$ in the sense of type theory'' implies
that there actually exists an element~$x$. In contrast, \notnot existence does
not.} And while Hilbert's basis theorem, stating that if a ring~$B$ is
Noetherian then so is the polynomial ring~$B[X]$, does have a constructive
proof for the anonymous version of the Noetherian condition,\footnote{For
instance, a careful reading of the textbook proof given
in~\cite[Theorem~7.5]{atiyah-macdonald:commutative-algebra} shows that the
basis theorem holds intuitionistically as stated.} this result seems empty: For
it just transforms one unconcrete promise (generators of each ideal of~$B$
exist somewhere, platonically) into another (generators for ideals of~$B[X]$
exist somewhere, platonically).

@@

\begin{remark}Given the importance of Theorem~\ref{thm:workhorse}, it is
natural to wonder where the proof stems from. Our proof proceeded in an ad hoc
fashion, verifying that the frame of radical ideals has the required properties
-- but where does the idea to use radical ideals come from? In general, determining the set
of provable sequents of a geometric theory is a challenging problem. Our most
efficient tool is probably the theory of \emph{entailment relations}. We refer
to Refs.~\bracketedrefcite{rinaldi-schuster-wessel:edde,cederquist-coquand:entrel} and
the references therein and also strongly recommend the literature on dynamical
methods in commutative
algebra~\bracketedrefcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,coquand:site}.
\end{remark}

@@

\paragraph{Grothendieck's generic freeness lemma.} This theorem is a basic
theorem in algebraic geometry, used for instance for developing the theory of
moduli spaces. When phrased for the affine situation in a constructively
sensible way, a simple version of this theorem reads as follows. We recall
from Section~\ref{sect:algebraic-preliminaries} that
the notation~$M[f^{-1}]$ makes sense for any element~$f \in A$; in case~$f$ is
zero or nilpotent, the localized module~$M[f^{-1}]$ will be the trivial module.\par
\begin{quote}
\textbf{Theorem.}
Let~$A$ be a reduced ring. Let~$M$ be a finitely generated~$A$-module.
If~$f = 0$ is the only element of~$A$ such that~$M[f^{-1}]$ is a
free~$A[f^{-1}]$-module, then~$1 = 0$ in~$A$.
\end{quote}
This theorem is particularly interesting for the program of constructivizing
classical commutative algebra, as it is an example where the constructive proof
is much shorter and arguably more perspiciuous than classical proofs (for which
see for instance Refs.~\cite[Lemme~6.9.2]{ega-4-2},
\cite[Thm.~24.1]{matsumura:commutative-ring-theory} or
\cite[Thm.~14.4]{eisenbud:commutative-algebra}, which only cover the case of
Noetherian integral domains, or Refs.~\bracketedrefcite{staats:generic-freeness},
\cite[Tag~051Q]{stacks-project}
which proceed in a series of intermediate steps, reducing to that case).\par
\begin{quote}
\textbf{Proof.} By Example~\ref{ex:negneg-interpretation} and
Exercise~\ref{ex:bridging-modules}(\ref{item:free}), the claim amounts to the statement that~$M^\sim$ is \notnot
free. Since~$A^\sim$ is a field, this statement follows from
basic (intuitionistic) linear algebra.\footnote{A standard result of linear
algebra is: ``Any finitely generated vector space over a field is finite free
(that is, has a finite basis).'' The proof proceeds by considering a given
generating family and using the law of excluded middle to determine whether one
of the generators can be expressed using the others or not. In the latter case,
the family is linearly independent and hence a basis; in the former case, the
proof removes the redundant generator and continues by induction.

@@

Item~(1) is by basic linear algebra as in the proof of
simple version of Grothendieck's generic freeness lemma, but a bit more involved as we now need to
deal with countable generating
families~\cite[Theorem~11.16]{blechschmidt:phd}. Item~(2) is because finitely
generated algebras over anonymously Noetherian rings are \notnot finitely
presented (in a description of the form~$R[X_1,\ldots,X_n]/\aaa$, the
ideal~$\aaa$ is \notnot finitely generated).
Item~(3) is because finitely generated modules over anonymously Noetherian are
\notnot finitely presented.\qed
\end{quote}
A variant of this proof where the reference to the Noetherian condition has
been replaced by an explicit computation has been unwound in
Ref.~\bracketedrefcite{blechschmidt:generic-freeness}.

@@

Other short and explicit proofs of McCoy's theorem are given in
Refs.~\bracketedrefcite{blocki:mccoy},
\cite[Theorem~5.22]{lombardi-quitte:constructive-algebra} and
\cite[Exercise~5.23A(3)]{lam:exercises}. The proof in
Ref.~\cite[Proposition~III.8.2.3]{bourbaki:alg} employs the law of excluded
middle. We were not able to discern that these proofs are just different
presentations of the same idea that ours is based on; these proofs all employ
computations with Cramer-like formulas, while our proof stresses the similarity
to the field case.

@@

The for these purposes correct constructive notion of Krull dimension can be
found in Refs.~\bracketedrefcite{coquand-ducos-lombardi-quitte:krull-integral,coquand-lombardi-roy:char-krull}.
It has been used to give a short and constructive proof that~$\dim
k[X_1,\ldots,X_n] = n$, where~$k$ is a geometric
field~\cite{coquand-lombardi:krull-dim-polynomial-ring}. Proofs of the stated
relation between the dimension of~$A$ and the dimension of~$A^\sim$ are recorded in
Ref.~\cite[Section~3.4]{blechschmidt:phd}.\par}
\end{exercise}

@@

{\scriptsize\emph{Note.} A self-contained solution is given in
Ref.~\bracketedrefcite{blechschmidt:kaplansky}.\par}
\end{alphlist}
\end{exercise}
